Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-03-25 Ben_Manuscripts/transport/Outline.tex
comments.
Figure and organization updates

%BJC: potential titles (uncommented is current favorite)
%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\title{Chemically Dependent Selectivity in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

%  There are a number of questions that we wish to answer in order to create a
%  framework for studying this system in even greater detail.
  \noindent There are a number of questions we wish to address in order to characterize
  transport in this system.
  \begin{enumerate}

   	\item What transport mechanisms do we observe? \label{question:mechanisms}

  	Given that the pores will restrict motion of the solutes, we anticipate that 
  	transport will be hindered in some way. We want to understand the differences in
  	solute motion, specifically its mean squared displacement (MSD), based on a solute's
  	size, shape and chemical functionality. We will study the interactions
  	between solutes, the membrane, and water in order to determine which mechanism
  	or mechanisms dominate.

  	\item How do molecules, including water, partition within the pores? \label{question:partition}

  	From a macroscopic perspective, it is straightforward to hypothesize that the water and
  	polar solutes spend their time exclusively in the tube-like hydrophilic pore region.
  	Our previous work showed that there is a gradual compositional transition from the 
  	hydrophilic to the hydrophobic region which means that solutes may not 
  	necessarily stay confined to the centers of the pores or even within the
  	pore region. We will study the gradient in composition of solutes and water
  	and any resultant influence it might have on mechanistic properties.

%  	\item Can we describe the transport mechanisms using pre-existing 
%  	mathematical models. \label{question:math}
%  	
%  	A mathematical model may provide additional insight into the transport
%  	mechanisms and, in future work, can help relate performance on the 
%  	timescales studied with MD to macroscopic timescales. We will use
%  	qualitative and semi-quantitative arguments in order to choose a 
%  	governing model.

  	\item How can we modify the current monomers in order to enhance
  	solute-specific separations? \label{question:math}

  	Most experimental characterization up to this point has been centered 
  	around the monomer, Na-GA3C11, studied here. The primary reason for conducting
  	these simulations is to understand what chemical modifications can be made 
  	to this or similar liquid crystal molecules in order to enhance transport 
  	of desired species or restrict that of undesired species. We will use the 
  	insight gained from our mechanistic observations in order to suggest new 
  	monomer designs.

  \end{enumerate}

@@

  %BJC: reference to supporting info with more details on water partition
  %BJC: or should that go in the main body results?
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
	\item There is a 2:1 ratio of water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
	\item See section~\ref{S-section:water_content_equil} of the SI for further details on 
	water equilibration in this system.
	\item We iteratively adjusted the pore radius in our systems until the right amount of water
	fit in the pores when we ran \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
  \end{itemize}

@@

  \noindent We measured the time-averaged $z$-direction mean squared 
  displacement (MSD) of the centers of mass of each solute over the 
  course of 1 $\mu$s MD simulations using Equation~\ref{eqn:tamsd}.
  \begin{itemize}
    \item \begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\label{eqn:tamsd}
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
	\item Generally, the MSD grows according to Equation~\ref{eqn:msd_form},
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	\item where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
	$\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
	motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
	\item In practice, $\alpha$ corresponds to the growth of the \textit{ensemble}
	MSD given by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
	\item The ensemble MSD is calculated with respect to a reference position and
	hence carries some dependence on its starting point.
	\item The time-averaged MSD averages over all possible time lags of a given 
	length, effectively eliminating any initial configuration dependence and generating
	an increased number of observations. 
	\item For ergodic systems, both types of MSDs will be equal.
	\item Since we have a small number of solutes with which to generate statistics
	and because we are not calculating values for $\alpha$ in this particular study,
	we will only use the time-averaged MSD.
  \end{itemize}

@@

  In order to determine an effective radius for each solute, we measured the 
  maximum pairwise distance between atoms of each solute over the course of
  a 2.5 ns simulation of solutes dissolved in a cubic box of water.
  \begin{itemize}
    \item Each box consisted of about 2100 water molecules and 6 solutes.
    \item Although there exist more involved methods for determining the 
    hydrodynamic radius~\cite{schultz_determination_1961}, we chose to use
    a simpler and more intuitive metric since we are only interested in
    observing trends in the solute mean squared displacement as a function
    of solute size. 
  \end{itemize}

@@

  \subsection*{Radial Density Functions}\label{method:rdfs}
  % BJC1: Should it be Radial Distribution Functions?

@@

  %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
  %we are not picking and choosing results (either consciously or unconsciously) 
  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    \item In section~\ref{S-section:hbond_sensitivity} of the SI, we show that our 
    conclusions are insensitive to this definition within a reasonable range.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

@@

  %BJC: Do analysis on pure water system for this section.

@@

  % BJC1: Should I show a dry system?
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.415\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.15\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.415\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}

  %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
  %BJC1: tried it out. Seems like a good addition.
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  All RDFs represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin to which they belong. The pores of the 5 
  wt \% system (a) appears to be much more crowded by monomers than the 10 wt \% system (b).
  Head groups in (a) are densest about 0.2 nm closer to the pore center than in (b). 
  A small amount of tail components find their way close to the pore center of the 5 wt \% system.
  }\label{fig:component_densities}
  \end{figure}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item Compared to 3.4 coordinated water molecules in bulk solution (see 
    section~\ref{method:coordination}), sodium ions in our system are, on average,
    coordinated to about 1.7 water molecules in the 10 wt \% system and 1.2 water
    molecules in the 5 wt\% system.
    \item The low levels of water coordination under confinement are likely driven
    in part by favorable interactions between sodium ions and carboxylate head groups.
    \item A dehydrated sodium ion is not well shielded from the negatively charged 
    carboxylate group.~\cite{ma_drastically_2019}. 
    \item On average, sodium ions coordinate with 0.5 carboxylate group oxygen atoms in the
    10 wt \% water system and 0.4 carboxylate oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  %BJC: missing a few since those simulations just got started
  %BJC1: wondering if I should add some kind of confidence interval to the Stoke-Einstein plots. Based on the errorbars of methanol
  %BJC1: should the points be labeled with residue names?
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.}\label{fig:msds}
  \end{figure}  
  %MRS1: Having so much data here grapically is nice. ought to think how else data can be displayed. Perhaps figures with the dwell times as well?  Depends on if those are being shown.  2D scatter plots with average partitioning distance of solute vs. MSD? We should keep brainstorming which will be most relevant. 
  \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
  %, providing the beginnings of an answer to question~\ref{question:mechanisms}.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass in the 10 wt \% water system.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in 
	Figure~\ref{fig:example_msd} and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

@@

  Finally, we see instances of solutes that become immobilized or slowed by 
  association with sodium counterions. 
  \begin{itemize}
    \item Much like water, the polarity of the solutes creates regions of high
    electron density, modeled using partial negative charges, which are stabilized
    through electrostatic interactions with sodium ions.
    \item There are many cases in which polar groups bind to sodium ions for at
    least a short period of time. 
    \item There are some cases where solutes become immobilized for long periods
    of time while in close proximity to a sodium ion.
    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
    within 2.5 \AA~of a sodium ion for the entire length of a trapping occurence.
  \end{itemize}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
  the majority of the trapping occurence between 400 and 600 ns. Regions
  highlighted red or blue indicate times when methanol's oxygen atom is within 
  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  % BJC: This might be better cut off at y ~ 0.6 and then provide an inset with full RDFs
  \includegraphics[width=\linewidth]{polyols_rdf.pdf}
  \caption{}\label{fig:polyols_rdf}
  \end{subfigure}
  \begin{subfigure}{0.50\textwidth}
  \vspace{-0.275cm}
  \includegraphics[width=\linewidth]{multi_hbonds.pdf}
  \caption{}\label{fig:multi_hbonds}
  \end{subfigure}
  % BJC: this subfigure is probably best suited for the supporting information.
%  \begin{subfigure}{\textwidth}
%  \centering
%  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
%  \caption{}\label{fig:dwell_hop_PG_GCL}
%  \end{subfigure}
  \caption{(a) Glycerol, tetrose and ribose are densest close to the pore center because
  they have a high number of hydrophilic groups and are relatively large. Ethylene glycol
  and propylene glycol are densest close to the head group region. (b) The number of 
  hydrogen bond interactions between solutes and monomers increases as solutes gain additional
  hydroxyl groups. The number of hydrogen bonds made by a single solute in different locations
  simultaneously, n, also increases with the number of hydroxyl groups. In the most extreme case,
  all four hydroxyl groups of Ribose (n = 4) are involved in a hydrogen bond interaction at
  the same time.}\label{fig:multi_hbonds}
  \end{figure}

@@

  \noindent Solutes do not make frequent hops while in the pore region.
  \begin{itemize}
	\item Observations of single THF trajectories have revealed that it becomes 
	nearly immobilized while associated with sodium ions 
	(See Figure~\ref{fig:thf_sodium_coordination}).
	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
	higher than THF near the head groups. The planar shape of DMF causes it to 
	become stuck between head groups. Excursions into the pore region do not
	necessarily result in large hops.
  \end{itemize}

@@

  %All have comparable densities near pore center except acetone which is lower

  \subsection{Design Considerations}

>>>>

%BJC: potential titles (uncommented is current favorite)
%\title{The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
%\title{Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\title{Chemically Dependent Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane}
\author{Benjamin J. Coscia \and Michael R. Shirts}

@@

  %BJC2: Changed format from numbered questions to more of a roadmap for this paper

  First, we will comment on the membrane's structure.
  \begin{itemize}
    \item We have previously studied dry membrane systems and some systems with
    low water content.
    \item We will observe how the radial density of monomer components and water
    change based on membrane water content.
  \end{itemize}

  Then we will present our efforts to understand how small molecules, including water
  partition within the pores?
  \begin{itemize}
    \item From a macroscopic perspective, it is straightforward to hypothesize that 
    the water and polar solutes spend their time exclusively in the tube-like hydrophilic
    pore region.
    \item Our previous work showed that there is a gradual compositional transition 
    from the hydrophilic to the hydrophobic region which means that solutes may not 
    necessarily stay confined to the centers of the pores or even within the
    pore region. 
    \item We will study the gradient in composition of solutes and water and any 
    resultant influence it might have on mechanistic properties.
  \end{itemize}

  Finally, and for the bulk of this work, we will present our observations and explantions
  of the various transport mechanisms exhibited by water and solutes.
  \begin{itemize}
    \item Given that the pores will restrict motion of the solutes, we anticipate that 
    transport will be hindered in some way. 
    \item We want to understand the differences in solute motion, specifically its mean
    squared displacement (MSD), based on a solute's size, shape and chemical functionality.
    \item We will study the interactions between solutes, the membrane, and water in order
    to determine which mechanism or mechanisms dominate.
  \end{itemize}

%  There are a number of questions that we wish to answer in order to create a
%  framework for studying this system in even greater detail.
%  \noindent There are a number of questions we wish to address in order to characterize
%  transport in this system.
%  \begin{enumerate}
%  
%   	\item What transport mechanisms do we observe? \label{question:mechanisms}
%  	
%  	Given that the pores will restrict motion of the solutes, we anticipate that 
%  	transport will be hindered in some way. We want to understand the differences in
%  	solute motion, specifically its mean squared displacement (MSD), based on a solute's
%  	size, shape and chemical functionality. We will study the interactions
%  	between solutes, the membrane, and water in order to determine which mechanism
%  	or mechanisms dominate.
%  
%  	\item How do molecules, including water, partition within the pores? \label{question:partition}
%  	
%  	From a macroscopic perspective, it is straightforward to hypothesize that the water and
%  	polar solutes spend their time exclusively in the tube-like hydrophilic pore region.
%  	Our previous work showed that there is a gradual compositional transition from the 
%  	hydrophilic to the hydrophobic region which means that solutes may not 
%  	necessarily stay confined to the centers of the pores or even within the
%  	pore region. We will study the gradient in composition of solutes and water
%  	and any resultant influence it might have on mechanistic properties.
%  	
%%  	\item Can we describe the transport mechanisms using pre-existing 
%%  	mathematical models. \label{question:math}
%%  	
%%  	A mathematical model may provide additional insight into the transport
%%  	mechanisms and, in future work, can help relate performance on the 
%%  	timescales studied with MD to macroscopic timescales. We will use
%%  	qualitative and semi-quantitative arguments in order to choose a 
%%  	governing model. 
%  	
%        %MRS2: this is beyond the scope of what we can really answer. We can hypothesize things, but 
%        % we really haven't really done any experiments to confirm these.  So this should be deemphasized.
%  	\item How can we modify the current monomers in order to enhance
%  	solute-specific separations? \label{question:math}
%  	
%  	Most experimental characterization up to this point has been centered 
%  	around the monomer, Na-GA3C11, studied here. The primary reason for conducting
%  	these simulations is to understand what chemical modifications can be made 
%  	to this or similar liquid crystal molecules in order to enhance transport 
%  	of desired species or restrict that of undesired species. We will use the 
%  	insight gained from our mechanistic observations in order to suggest new 
%  	monomer designs.
%  	
%  \end{enumerate}

@@

  %BJC: reference to supporting info with more details on water partition
  %BJC: or should that go in the main body results?
  %MRS2: depends on whether it's necessary to support the main hypothesis. 
  %BJC2: made more vague and included specifics in membrane structure section
  We observed that water partitions into the tail region of our system and therefore
  built our initial configurations with water in both regions close to the expected
  equilibrium value.
  \begin{itemize}
    \item We define the partition between the pore and tail region to be ca. 1.5 nm from
    the pore center based on the minimum in the radial distribution of water (See section~\ref{method:rdfs}).
%	\item There is a 2:1 ratio of water in the pores versus in the tails for the 10 wt \% system.
	\item The amount of water present in the tails may or may not be experimentally consistent
	but if we don't put it in, the results will not be thermodynamically consistent, which 
	will give issues with measurements and calculations.
%	\item See section~\ref{S-section:water_content_equil} of the SI for further details on 
%	water equilibration in this system.
	\item We iteratively adjusted the pore radius in our systems until the right amount of water
	fit in the pores when we ran \texttt{gmx solvate}.
	\item We placed water molecules in the tail region one at a time in random locations
	with short energy minimizations between insertions.
	\item When studying transport of water in the pores, we limited the calculations
	to water molecules that spend greater than 95 \% of their time in the pore region.
  \end{itemize}

@@

  \noindent We measured the time-averaged $z$-direction mean squared 
  displacement (MSD) of the centers of mass of each solute over the 
  course of 1 $\mu$s MD simulations using Equation~\ref{eqn:tamsd}.
  \begin{itemize}
    \item \begin{equation}
	\overline{x^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (x(t + \tau) - x(t))^2 dt
	\label{eqn:tamsd}
	\end{equation}
	where $\tau$ is the time lag and T is the length of the
	trajectory~\cite{meroz_toolbox_2015}. 
	\item Generally, the MSD grows according to Equation~\ref{eqn:msd_form},
	\begin{equation} 
	\langle x^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
	\end{equation} 
	\item where $\alpha$ is the anomalous exponent and $K_\alpha$ is the
	generalized diffusion coefficient.
	\item A value of $\alpha < 1$ indicates a subdiffusive process, while a value of
	$\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
	motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
	\item In practice, $\alpha$ corresponds to the growth of the \textit{ensemble}
	MSD given by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
	\begin{equation}
	\langle x^2(t) \rangle = \langle x(t) - x(0) \rangle
	\label{eqn:ensemble_msd}
	\end{equation}
	\item The ensemble MSD is calculated with respect to a reference position and
	hence carries some dependence on its starting point.
	\item The time-averaged MSD averages over all possible time lags of a given 
	length, effectively eliminating any initial configuration dependence and generating
	an increased number of observations. 
	\item For ergodic systems, both types of MSDs will be equal.
	\item Since we have a small number of solutes with which to generate statistics
	and because we are not calculating values for $\alpha$ in this particular study,
	we will only use the time-averaged MSD.
  \end{itemize}

@@

  In order to determine an effective radius for each solute, we measured the 
  maximum pairwise distance between atoms of each solute over the course of
  a 2.5 ns simulation of solutes dissolved in a cubic box of water.
  % MRS2: this might be slightly larger than the hydrodynamic radius?  We might not be able to place it 
  % directly into stoke-einstein.
  % BJC2: Yeah, I've thought about this. Actually calculating the hydrodynamic
  % radius would involve a viscosity calculation (which I have the tools to do)
  \begin{itemize}
    \item Each box consisted of about 2100 water molecules and 6 solutes.
    \item Although there exist more involved methods for determining the 
    hydrodynamic radius~\cite{schultz_determination_1961}, we chose to use
    a simpler and more intuitive metric since we are only interested in
    observing trends in the solute mean squared displacement as a function
    of solute size. 
  \end{itemize}

@@

  \subsection*{Radial Distribution Functions}\label{method:rdfs}

@@

  %MRS1: We want to be able to say that conclusions are independent of reasonable changes in the definition so
  %BJC2: sensitivity added to supporting information
  %we are not picking and choosing results (either consciously or unconsciously) 
  Based on the geometric criteria proposed by Luzar and Chandler \cite{luzar_effect_1996},
  we determined a hydrogen bond to exist if the distance between the donor, D, and acceptor,
  A, atoms is less than 3.5 \AA~and the angle formed by D--H...A is less than 30\degree.
    %BJC: According to Luzar/Chandler: The range of a water molecule’s first coordination
    % shell is 3.5 Å, as determined from the oxygen-oxygen radial distribution function.
    % The amplitude of librations that break hydrogen bonds is ,~ 30 degrees, as estimated
    % from Debye-Waller factors
  \begin{itemize}
    \item Attempts to describe a hydrogen bond in the context of molecular simulations has
    yielded a number of definitions with no true consensus \cite{prada-gracia_quest_2013}.
	\item The geometry of hydrogen bonds has some dependence on the system being studied. 
    \item The definition of Luzar and Chandler is easily visualized for trajectories using
    the \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
    package which allows us to directly check the validity of identified hydrogen bonds.
    \item In section~\ref{S-section:hbond_sensitivity} of the SI, we show that our 
    conclusions are insensitive to this definition within a reasonable range.
    %BJC: might need to update this if something better exists for nitrogen 
  \end{itemize}

@@

  %TODO redo analysis on pure water system for this section.

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.415\textwidth}
  \includegraphics[width=\textwidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.15\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
  \label{fig:monomer_color_coded}
  \end{subfigure}
  \begin{subfigure}{0.415\textwidth}
  \includegraphics[width=\textwidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  %MRS1: possibly include vertical dotted line to show where max head group peak occurs.
  %BJC1: tried it out. Seems like a good addition.
  %MRS2: I wonder to what extent it would help to show the curves on top of each other to make it clear
  %how much things are displaced.
  %BJC2: I'll see what I can do without overly cluttering the figure
  \caption{The radial densities of various monomer components paint a picture of the
  pore topology where the pore centers are primarily composed of water and sodium ions.
  All RDFs represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin to which they belong. The pores of the 5 
  wt \% system (a) appears to be much more crowded by monomers than the 10 wt \% system (b).
  Head groups in (a) are densest about 0.2 nm closer to the pore center than in (b). 
  A small amount of tail components find their way close to the pore center of the 5 wt \% system.
  }\label{fig:component_densities}
  \end{figure}

  There is an appreciable amount of water that partitions into the tail region of both
  systems.
  \begin{itemize}
    \item 28 \% and 31 \% of the total water is present in the tail regions of the 5 and 
    10 wt\% water systems respectively 
    \item See section~\ref{S-section:water_content_equil} of the SI for more details.
    \item This result is likely due to a combination of the lower density of the tail region
    and oxygen atoms at the ends of each monomer tail which can stabilize water molecules. %TODO Total density as function of distance from pore center.
  \end{itemize}

@@

  \noindent Sodium coordinates with far less water molecules than it does in 
  bulk solution.
  \begin{itemize}
    \item Compared to 3.4 coordinated water molecules in bulk solution (see 
    section~\ref{method:coordination}), sodium ions in our system are, on average,
    coordinated to about 1.7 water molecules in the 10 wt \% system and 1.2 water
    molecules in the 5 wt\% system.
    \item However, the sodium ions are not undercoordinated since they frequently 
    pair with carboxylate head groups.
    %MRS2: might need to point out that they are not that undercoordinated, as they also coordinate with solutes.
    %BJC2: not solutes here, because the final calculations will be done for a pure water system.
%    \item The low levels of coordination with water under confinement are likely driven
%    in part by favorable interactions between sodium ions and carboxylate head groups.
%    \item A dehydrated sodium ion is not well shielded from the negatively charged 
%    carboxylate group.~\cite{ma_drastically_2019}. 
    \item On average, sodium ions coordinate with 0.5 carboxylate group oxygen atoms in the
    10 wt \% water system and 0.4 carboxylate oxygen atoms in the 5 wt \% water system. 
    % BJC: I thought 5 wt \% might be a little higher. These numbers might be skewed by
    % sodium ions that are within cutoff of both carboxylate oxygen atoms. Might be
    % better to report average number of sodiums coordinated to a head group
  \end{itemize}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_5wt_tamsds.pdf}
  \caption{5 wt \% water}\label{fig:all_msds_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds.pdf}
  \caption{10 wt \% water}\label{fig:all_msds_10wt}
  \end{subfigure}
  %BJC1: wondering if I should add some kind of confidence interval to the Stoke-Einstein plots. Based on the errorbars of methanol
  %MRS2: probably, perhaps as a colored background.  But might make it too noisy to read.  MAybe color them by chemical group?
  %BJC1: should the points be labeled with residue names?
  %MRS2: as long as there is a table in SI with the relevant information, probably isn't needed.  That would also make it hard to read the plot.   
  %MRS2: for the plots with fewer points (like alcohol), the individual points should be labeled, there is room.
  %MRS2: as discussed, maybe for each solute group, have a MSD plot a) and RDF plt b) and other important plots in c) and d)
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_5wt.pdf} 
  \caption{5 wt \% water}\label{fig:msd_radius_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{msd_radius_10wt.pdf} 
  \caption{10 wt \% water}\label{fig:msd_radius_10wt}
  \end{subfigure}
  \caption{The MSDs of solutes in the 5 wt \% water system (a) are significantly
  smaller than those of the solutes in the 10 wt \% water system (b). The
  MSDs are not a monotonic function of molecular size (c and d). A significant
  number of solute MSDs fall below the theoretical lines predicted by the 
  Stokes-Einstein equation and Gierer and Wirtz' corrected Stokes-Einstein equation.}\label{fig:msds}
  \end{figure}  
  %MRS1: Having so much data here grapically is nice. ought to think how else data can be displayed. Perhaps figures with the dwell times as well?  Depends on if those are being shown.  2D scatter plots with average partitioning distance of solute vs. MSD? We should keep brainstorming which will be most relevant. 
  \noindent On the timescales simulated in our study, solutes exhibit subdiffusive behavior.
  \begin{itemize}  
    \item Figure~\ref{fig:example_ztraces} plots the $z$-coordinate versus time of
  	3 representative ethanol centers of mass in the 10 wt \% water system.
  	\item There are clear periods of entrapment separated by relatively large hops.
	\item The MSD calculated based on all ethanol molecules is plotted in 
	Figure~\ref{fig:example_msd} and is sublinear.
	\item The long periods of entrapment likely lead to this sublinear, and thus
	subdiffusive, behavior.
  \end{itemize}

@@

  Finally, we see instances of solutes that become immobilized or slowed by 
  association with sodium counterions. 
  \begin{itemize}
    \item Much like water, the polarity of the solutes creates regions of high
    electron density, modeled using partial negative charges, which are stabilized
    through electrostatic interactions with sodium ions.
    \item There are many cases in which polar groups bind to sodium ions for at
    least a short period of time. 
    \item Some kind of pair time distribution  %TODO
%    \item There are some cases where solutes become immobilized for long periods
%    of time while in close proximity to a sodium ion.
%    \item In Figure~\ref{fig:na_met_trace}, the oxygen atom of methanol stays
%    within 2.5 \AA~of a sodium ion for the entire length of a trapping occurence.
  \end{itemize}

  % BJC2: moved to supporting since anecdotal
%  \begin{figure}[!htb]
%  \centering
%  %MRS2: would be better if this was paired with ensemble data, instead of just one trajectory.
%  \includegraphics[width=0.45\textwidth]{na_met_trace.pdf}  % create with nn.py located in MET/10wt
%  \caption{The oxygen atom of methanol stays within 2.5 \AA~of the same sodium ion for
%  the majority of the trapping occurence between 400 and 600 ns. Regions
%  highlighted red or blue indicate times when methanol's oxygen atom is within 
%  2.5 \AA~of a sodium ion. The color of the shaded regions are switched every time
%  the oxygen atom becomes associated to a different sodium ion.}\label{fig:na_met_trace}
%  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{msd_radius_diols_10wt.pdf}
  \caption{}\label{fig:polyols_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{polyols_rdf.pdf}
  \caption{}\label{fig:polyols_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \vspace{-0.275cm}
  \includegraphics[width=\linewidth]{multi_hbonds.pdf}
  \caption{}\label{fig:multi_hbonds}
  \end{subfigure}
  % BJC: this subfigure is probably best suited for the supporting information.
%  \begin{subfigure}{\textwidth}
%  \centering
%  \includegraphics[width=0.9\linewidth]{dwell_hop_PG_GCL.pdf}
%  \caption{}\label{fig:dwell_hop_PG_GCL}
%  \end{subfigure}
%MRS2: maybe include the MSD vs size plot subset here. 
  \caption{(a) Glycerol, tetrose and ribose are densest close to the pore center because
  they have a high number of hydrophilic groups and are relatively large. Ethylene glycol
  and propylene glycol are densest close to the head group region. (b) The number of 
  hydrogen bond interactions between solutes and monomers increases as solutes gain additional
  hydroxyl groups. The number of hydrogen bonds made by a single solute in different locations
  simultaneously, n, also increases with the number of hydroxyl groups. In the most extreme case,
  all four hydroxyl groups of Ribose (n = 4) are involved in a hydrogen bond interaction at
  the same time.}\label{fig:multi_hbonds}
  \end{figure}

@@

  \noindent Solutes do not make frequent hops while in the pore region.
  %MRS2: is this because you need H-bonding to make hops? We should have some sense of this.
  \begin{itemize}
%	\item Observations of single THF trajectories have revealed that it becomes 
%	nearly immobilized while associated with sodium ions 
%	(See Figure~\ref{fig:thf_sodium_coordination}).
	\item DMF experiences a similar effect, but to a lesser extent. Its density is 
	higher than THF near the head groups. The planar shape of DMF causes it to 
	become stuck between head groups. Excursions into the pore region do not
	necessarily result in large hops.
  \end{itemize}

@@

  %All have comparable densities near pore center except acetone which is lower
%
%  \subsection{Design Considerations}

  %MRS2: should be a bit careful on what WILL happen, as opposed to what might happen.
  %BJC2: condensed and added to conclusions.
